Finding Subgraphs With Side Constraints

### 2020-12-05 paper.tex
More words and plots

\title{Subgraph Isomorphism With Side Constraints}
\author{
    \"Ozg\"ur Akg\"un\inst{1} \and Jessica Enright\inst{2} \and Christopher
    Jefferson\inst{1} \and Ciaran McCreesh\inst{2} \and Patrick
    Prosser\inst{2} \and Steffen Zschaler\inst{3} \\
}
\authorrunning{\"O. Akgun et al.}
\institute{
    University of St Andrews, Scotland \and
    University of Glasgow, Scotland \\ \email{ciaran.mccreesh@glasgow.ac.uk} \and
    King's College London, England
}

>>>>

\title{Finding Subgraphs With Side Constraints}
\author{
    \"Ozg\"ur Akg\"un\inst{1} \and Jessica Enright\inst{2} \and Christopher
    Jefferson\inst{1} \and Ciaran McCreesh\inst{2} \and Patrick
    Prosser\inst{3} \and Steffen Zschaler\inst{4} \\
}
\authorrunning{\"O. Akgun et al.}
\institute{
    University of St Andrews, Scotland \and
    University of Glasgow, Scotland \\ \email{ciaran.mccreesh@glasgow.ac.uk} \and
    Algorithmicists Anonymous (Machrihanish), Scotland \and
    King's College London, England
}
